plots with prolactin

### 2020-04-11 analysis/16_PRL.Rmd
differnt  analysis with log counts

>>>>

```{r include=F, eval=F}
# data from VF
library(tidyverse)
counts <- read_csv("../results/2020-04-10_Suzanne_gene_counts_VF.csv") %>%
  mutate(logcounts = log(counts)) %>%
  select(bird_id, sex, tissue, stage, timept, geneid, counts, logcounts) %>%
  drop_na()
head(counts)

counts %>%
  filter(geneid == "prl") %>%
  ggplot(aes(x = as.factor(timept), y = logcounts)) +
  geom_boxplot(aes(color = sex)) +
  facet_wrap(~ tissue)
```
